The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-03 outputs/paper/paper.Rmd
rename variables

urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
population <- data.frame(group = c(rep("urban-rural", 2), rep("region", 5), rep("education", 4), rep("religion", 3)),
                                           Variable = data$Variable, 
                         Population = data$Number_of_Children) %>% head(-1)
population$Variable <- factor(population$Variable,
                              levels = population$Variable) %>% fct_rev()
```

>>>>

# Separate the dataset by category and lengthen the dataset by moving a column to row for easier plotting.
urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value") %>%
  mutate(immune_status = recode(immune_status, Health_Record = "Health Record", Mothers_Report = "Mother's Report", Not_Received_Immunization = "No Immunization"))
region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value") %>%
  mutate(immune_status = recode(immune_status, Health_Record = "Health Record", Mothers_Report = "Mother's Report", Not_Received_Immunization = "No Immunization"))
education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value") %>%
  mutate(immune_status = recode(immune_status, Health_Record = "Health Record", Mothers_Report = "Mother's Report", Not_Received_Immunization = "No Immunization"))
religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value") %>%
  mutate(immune_status = recode(immune_status, Health_Record = "Health Record", Mothers_Report = "Mother's Report", Not_Received_Immunization = "No Immunization"))
total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value") %>%
  mutate(immune_status = recode(immune_status, Health_Record = "Health Record", Mothers_Report = "Mother's Report", Not_Received_Immunization = "No Immunization"))
population <- data.frame(group = c(rep("urban-rural", 2), rep("region", 5), rep("education", 4), rep("religion", 3)),
                                           Variable = data$Variable, 
                         Population = data$Number_of_Children) %>% head(-1)
population$Variable <- factor(population$Variable,
                              levels = population$Variable) %>% fct_rev()
```
